The effects of priming in human computation

### 2014-05-14 docs/publications/2014.05.9_pnas/pnas2.tex
remove grammer mistakes and awk areas in intro

Such platforms render human cognition as fluid a resource as compute cycles: 
it is available on demand in small units, with low transaction cost, from 
anywhere via the Internet \footnote{\href{http://mturk.com}{http://mturk.com}}.
The task requestor can interact with the platform like a compute server, 
seamlessly 
integrating human and machine computation.  Researchers have put forward the 
term HPU (Human co-Processing Unit)\footnote{We acknowledge the irony of this 
term: the original meaning of `computer' was a person who performs 
computations, its reference to machines being a personification brought into 
usage in the late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
microtask platforms as a fundamentally new computing architecture
\cite{5543192}.

Originally used to distribute clerical work, these platforms 
increasingly serve as a cheap and fast means to engage experimental 
participants and provide qualitative annotations of datasets in a research 
setting \cite{snow2008cheap}.  Given the limited ability to screen workers, and their transient 
low-commitment engagement with the employer, researchers have criticized the
reliability of crowdsourced output \cite{marsden2009crowdsourcing}.

@@

Here we are concerned with effects of a more subtle origin: the influence that
prior tasks have on subsequent ones.  Psychology experiments document the 
strong effects that a prior exposure to stimulus can have on participants' 
performance in related tasks, a phenomenon known as \textit{priming}.  Strong 
priming effects have been demonstrated for
perceptual tasks such as the visual recognition of 
objects \cite{BJOP:BJOP1796},
auditory recognition of words \cite{BJOP:BJOP1826}, and the recognition
of gender* and affect*: precisely the kinds of tasks well-served by microtask 
platforms \cite{yuen2011survey, snow2008cheap}.

In this direction, researchers have investigated various effects due to 
\textit{framing}, by describing the larger workflow context in which the 
workers task is a part \cite{Kinnaird2012281}, or by describing the ultimate 
purpose of the project to provide meaning \cite{chandler2013breaking}.
It is certainly of value to investigate this kind of priming, but 
psychological experiments show that priming is strongest when 
delivered through the same modality as the task [***].  This leads us to 
investigate priming that occurs \textit{during} one task, influencing output
of subsequent similar tasks. We call such effects \textit{in-task priming}.

We investigate the effects of in-task priming on using an image-labeling task
on the AMT platform.  Each worker is required to label a \textit{prior set} of
images followed by a \textit{posterior set}, but no distinction is made between
these sets from the perspective of the worker.  The posterior set is
always the same, but workers are randomly assigned one of three prior sets.
We analyze the labels workers attribute to the posterior set to see if it is 
affected by the prior set.  We consider what aspects of image content the 
workers choose to label (the \textit{label orientation}), and on how specific 
the labels are (the \textit{label specificity}), both of which have direct 
consequence on the validity of using human computation to make qualitative 
judgments.

As a point of comparison, we subject some groups of workers to a kind of
framing: we disclose a fictitious, semantically-loaded name for the 
task-requestor, chosen to signal an interest in a specific aspect of the 
image content.  One might expect that this would strongly sway the labeling 
of the workers.  We detect the effects of these priming treatments, but 
remarkably, we find that in-task priming has a much stronger effect on label 
orientation and specificity.

@@

In psychology, priming is defined as the effect in which a prior stimulus leads
to faster or more accurate responses in a subsequent task than without the
stimulus, or where the stimulus allows the experimenter to the elicit 
responses from subsequent stimuli that are less intense or noisier [***].
We are interested in studying the effects of priming in a human computation
context, so we wish to adopt a more general view of priming as a kind of 
HPU hysteresis.  In our view, priming might have many effects other than
those normally measured.  We therefore require a more general definition and a 
more general tool for quantifying priming, suited to detecting general 
hysteresis effects.

>>>>

Such platforms render human cognition as fluid a resource as compute cycles: 
it is available on demand in small units, with low transaction cost, from 
anywhere via the Internet \footnote{\href{http://mturk.com}{http://mturk.com}}.
The task requester can interact with the platform like a compute server, 
seamlessly 
integrating human and machine computation.  Researchers have put forward the 
term HPU (Human co-Processing Unit)\footnote{We acknowledge the irony of this 
term: the original meaning of `computer' was a person who performs 
computations, its reference to machines being a personification brought into 
usage in the late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
microtask platforms as a fundamentally new computing architecture
\cite{5543192}.

Originally used to distribute clerical work, these platforms 
increasingly serve as a cheap and fast means to engage experimental 
participants and provide qualitative annotations of datasets in a research 
setting \cite{snow2008cheap}.  Given the limited ability to screen workers, and their transient 
low-commitment engagement with the requester, researchers have criticized the
reliability of crowdsourced output \cite{marsden2009crowdsourcing}.

@@

Here we are concerned with effects of a more subtle origin: the influence that
prior tasks have on subsequent ones.  Psychology experiments document the 
strong effects that a prior exposure to stimulus can have on participants' 
performance in related tasks, a phenomenon known as \textit{priming}[***].  
Strong 
priming effects have been demonstrated for
perceptual tasks such as the visual recognition of 
objects \cite{BJOP:BJOP1796},
auditory recognition of words \cite{BJOP:BJOP1826}, and the recognition
of gender[***] and affect[***]: precisely the kinds of tasks well-serviced by 
microtask platforms \cite{yuen2011survey, snow2008cheap}.

In the direction of priming, researchers have investigated various effects 
due to \textit{framing}, by disclosing to the worker the functional role of
their task in the workflow context \cite{Kinnaird2012281}, 
or describing a meaningful ultimate purpose of the project in which their
task is a part \cite{chandler2013breaking}.
However, psychological experiments show that priming is strongest when 
delivered through the same modality as the task [***].  This leads us to 
investigate how priming that occurs \textit{during} a task influences output
of subsequent similar tasks. We call such effects \textit{in-task priming}.

We investigate the effects of in-task priming for an image-labeling task
on the AMT platform.  Each worker is required to label a \textit{prior set} of
images followed by a \textit{posterior set}, but no distinction is made between
these sets from the perspective of the worker.  The posterior set is
always the same, but workers are randomly assigned one of three prior sets.
We analyze the labels workers attribute to the posterior set to see if it is 
affected by the prior set.  As effects, we consider what aspects of image 
content the workers choose to label (the \textit{label orientation}), and how 
specific the labels are (the \textit{label specificity}), both of which have 
direct consequence on the validity of using human computation to make 
qualitative judgments.

As a point of comparison, we subject some groups of workers to a kind of
framing: we disclose a fictitious, semantically-loaded name for the 
task-requester, chosen to signal an interest in a specific aspect of the 
image content.  One might expect that this would strongly sway the labeling 
of the workers.  We do detect the effects of framing, but, remarkably, we find 
that in-task priming has a much stronger effect on label orientation and 
specificity.

@@

In psychology, priming is defined as the effect in which a prior stimulus leads
to faster or more accurate responses in a subsequent task than without the
stimulus, or where the stimulus allows the experimenter to the elicit 
responses from subsequent stimuli that are less intense or noisier [***].
However priming might have many effects other than those traditionally 
measured.  We are interested in studying the effects of priming in a human 
computation, we adopt a more general view of priming as HPU hysteresis.
